---
title: "Take-home Exercise 6: Visualising and Analysing Community Network"
description: |
  This exercise is to find out the patterns in the social networks in the town, and describe ten significant patterns observed. 
author:
  - name: Huang Yaping
    url: https://www.linkedin.com/in/huang-yp/
    affiliation: School of Computing and Information Systems
    affiliation_url: https://scis.smu.edu.sg/
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Install packages
```{R}
packages = c('igraph', 'tidygraph', 'ggraph', 'visNetwork', 'lubridate', 'clock','tidyverse', 'ggmap')
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}

```

### Read small files
```{r}
participants <- read_csv("data/Participants.csv")
```

### Read big files; Data Wrangling to Aggregate the edges with weekdays, for August 2022, with weight > 3
```{r eval = FALSE}
Edges <- read_csv("data/SocialNetwork.csv")
Edges_summary_weekdays <- Edges %>% 
  mutate(date = ymd(timestamp)) %>% 
  mutate(weekday = wday(date, label= TRUE, abbr = FALSE)) %>% 
  mutate(month = month(date)) %>% 
  filter(month == 8) %>% 
  group_by(participantIdFrom, participantIdTo, weekday) %>% 
  summarise(Weight = n()) %>% 
  filter(participantIdFrom != participantIdTo) %>% 
  filter(Weight>3) %>% 
  ungroup 
write_rds(Edges_summary_weekdays, "data/rds/Edges_summary_weekdays.rds")
```
### Data Wrangling to derive Edges and Nodes on Monday
```{r}
Edges_summary_weekdays <- read_rds("data/rds/Edges_summary_weekdays.rds")

Edges_Mon <- Edges_summary_weekdays %>% 
  filter(weekday == "Monday")

write_rds(Edges_Mon, "data/rds/Edges_Mon.rds")
```

```{r}
Nodes_Mon <- data.frame(unique(unlist(Edges_Mon[1], Edges_Mon[2])))
colnames(Nodes_Mon)[1] <- "id"
```

```{r}
Nodes_Mon <- Nodes_Mon %>% 
  left_join(participants, by = c("id" = "participantId"))
```

### Build graph model for Monday

graph_from_data_frame() of igraph is used to covert the nodes and edges data.frame into an igraph file format. as_tbl_graph() converts network data and objects to a tidygraph data model.

```{r}
graph_Mon <- graph_from_data_frame(Edges_Mon,
                                   vertices = Nodes_Mon) %>% 
  as_tbl_graph()

graph_Mon
```

### Construct a basic network graph On Mondays of August
To reveal the relationship of education vs connectedness 

ggraph is an extension of the ggplot2 API tailored to graph visualizations and provides the same flexible approach to building up plots layer by layer.

```{R}
set.seed(123)
ggraph(graph_Mon,
       layout = "fr")+
  geom_edge_link()+
  geom_node_point(aes(colour = educationLevel))+
  facet_nodes(~educationLevel)+
  theme_graph()+
  ggtitle("Network Map on Monday of August - Education")
```
Note: the above network shows that low education residents are sparsely connected. 

### Construct a basic network graph On Mondays of August
To reveal the relationship of interest group vs connectedness 

```{R}
set.seed(123)
ggraph(graph_Mon,
       layout = "fr")+
  geom_edge_link()+
  geom_node_point(aes(colour = interestGroup))+
  facet_nodes(~interestGroup)+
  theme_graph()+
  ggtitle("Network Map on Monday of August - Interest Group")
```
Observation: interest group B, C, D, and J shows activities on Monday. 

### Data Wrangling to derive Edges and Nodes on Sunday
```{r}
Edges_Sun <- Edges_summary_weekdays %>% 
  filter(weekday == "Sunday")
```

```{r}
Nodes_Sun <- data.frame(unique(unlist(Edges_Sun[1], Edges_Sun[2])))
colnames(Nodes_Sun)[1] <- "id"
```

```{r}
Nodes_Sun <- Nodes_Sun %>% 
  left_join(participants, by = c("id" = "participantId"))
```

### Build graph model for Sunday
```{r}
graph_Sun <- graph_from_data_frame(Edges_Sun,
                                   vertices = Nodes_Sun) %>% 
  as_tbl_graph()

graph_Sun
```
### Construct network graph On Sundays of August for people with and without kids
To find out how kids status impact how people are connnected on Sunday

```{R}
set.seed(123)
ggraph(graph_Sun,
       layout = "fr")+
  geom_edge_link()+
  geom_node_point(aes(colour = haveKids))+
  facet_nodes(~haveKids)+
  theme_graph()+
  ggtitle("Network Map on Sunday of August - With kids vs Without Kids")
```
Observation: it can be seen that people with kids are less connected on Sunday. 

### Construct an interest group network graph On Sundays of August
To find out how people in different interest groups are connected. 

```{R}
set.seed(123)
ggraph(graph_Sun,
       layout = "fr")+
  geom_edge_link()+
  geom_node_point(aes(colour = interestGroup))+
  facet_nodes(~interestGroup)+
  theme_graph()+
  ggtitle("Network Map on Sunday of August - Interest Group")
```
Observation: it can be seen that the interest groups are slightly more connected on Sunday compared to Monday, espciallu group A. 


